---
title: "Modeling animal behavior from passive acoustic telemetry data"
output: html_notebook
---

This R notebook is designed to provide basic model fitting to acoustic telemetry data for the purpose of characterizing and quantifying movement patterns and behavior.


First we'll need to load in some data and set our directories
```{r}
load(file.path(project_dir, "workspace_image_updated"))
if(!file.exists('scratchpad')){
  dir.create(file.path(src_dir, 'scratchpad'))
}
setwd(file.path(src_dir, 'scratchpad'))
```


We also define some common objects from results from our workspace
```{r}
analysis_summary = phase_10_valid
vue_df = analysis_summary$data
tagging_df = analysis_summary$tagging_data
receiver_df = analysis_summary$receiver_data
```


We're interested in looking at how movement behavior patterns are affected by enviornmental co-variates. These include time of day, temperature, current direction, tide, and lunar phase. 

First lets look at time of day
```{r}
plot(cars)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

