---
title: "Diurnal Patterns in Space Use Behavior"
output: html_notebook
---

The purpose of this notebook is to test if the stations at which tagged opkapaka are detected changes at different times of day.

To accomplish this, we will construct a contingency table for each tagged fish. Rows will indicate each period of day and columns represent stations. Values will be the % of detections occurring at that station during that period.

We will then use a chi-squared test wether station use was homogenious or hetrogenius for that individual. Final results will be be presented as the ratio beteen these groups.

```{r}
#### Testing if individuals spend equal time in equal places
### This will be done with contingency tables and chi-squre tests
chisq_df = data.frame('tag_id' = unique(analysis_summary$data$tag_id), 'significant' = FALSE, 'n_stations' = 0, 'n_time_periods' = 0, stringsAsFactors = FALSE)
for(i in 1:length(unique(analysis_summary$data$tag_id))){
  # Subset individual data
  indv_data = analysis_summary$data[analysis_summary$data$tag_id == unique(analysis_summary$data$tag_id)[i] & analysis_summary$data$station != 'Tagging Location', ]
  # Create a contingency table of detections between time of day and station
  cont_table = table(indv_data$time_of_day, indv_data$station)
  # Standardize that contingency table so values are % of all detections at each station
  for(j in 1:nrow(cont_table)){
    cont_table[j, ] = (cont_table[j, ] / rowSums(cont_table)[j]) * 100
  }
  # Perform chi square test
  cont_chisq = chisq.test(cont_table)
  # Update main dataframe
  if(cont_chisq$p.value <= 0.05){
    chisq_df$significant[i] = TRUE
  }
  chisq_df$n_stations[i] = ncol(cont_table)
  chisq_df$n_time_periods[i] = nrow(cont_table)
}
print(paste('Of the', length(chisq_df$tag_id), 'tagged fish,', length(which(chisq_df$significant == TRUE)), 'had significant differences between the stations they visited during each period of the day.'))

```

How many of these fish made any movements?
```{r}
aggregate(analysis_summary$data$station[analysis_summary$data$station != 'Tagging Location'], by = list(analysis_summary$data$tag_id[analysis_summary$data$station != 'Tagging Location']), FUN = unique)
```


We'll now essentially cluster each fish's position during each period by finding the mean location in lat and lon space
```{r}
cluster_position = aggregate(analysis_summary$data$lon, by = list( analysis_summary$data$tag_id, analysis_summary$data$time_of_day), FUN = mean)

cluster_position$lat = aggregate(analysis_summary$data$lat, by = list( analysis_summary$data$tag_id, analysis_summary$data$time_of_day), FUN = mean)[ncol(cluster_position)]
colnames(cluster_position) = c('tag_id', 'time_of_day', 'mean_lon', 'mean_lat')

## Remove fish that did not significantly redistribute
cluster_position = cluster_position[cluster_position$tag_id %in% chisq_df$tag_id[chisq_df$significant == TRUE], ]
```

And now we can model this data to see if there are any changes
```{r}
lon_test = lmer(mean_lon ~ time_of_day + (1|tag_id), data = cluster_position)
summary(lon_test)

lat_test = lmer(mean_lon ~ time_of_day + (1|tag_id), data = cluster_position)
summary(lat_test)
```



Lets make 4 plots of the receiver network so we can compare the primary location of individuals across periods
```{r}
## Plot mean position by time of day
time_of_day_plot = autoplot(analysis_summary$bathymetry, geom = "contour") + 
  geom_point(data = analysis_summary$receiver_df[analysis_summary$receiver_df$recovered == "", ], aes(x = lon, y = lat), shape = 21, col = 'red', size = 8) +
  geom_jitter(data = cluster_position, aes(x = mean_lon, y = mean_lat, col = time_of_day), size = 5, shape = 19, width = .005, height = .005) + 
  geom_line(data = brfa_e[1:2, ], aes(x = lon, y = lat), col = 'purple') + 
  geom_line(data = brfa_e[2:3, ], aes(x = lon, y = lat), col = 'purple') + 
  geom_line(data = brfa_e[3:4, ], aes(x = lon, y = lat), col = 'purple') + 
  labs(color = 'Time of Day', x = 'lon', y = 'lat') + theme_classic()


pdf('Mode Locations by Diurnal Period.pdf')
  print(time_of_day_plot)
dev.off()
```
